\chapter*{Preface\markboth{Preface}{Preface}}\label{ch:preface}
This report documents the 6th semester Medialogy bachelor project committed in the period February to May 2017 by Christina Kristensen, Emilie Lind Damkjær, Liv Arleth, and Margarita Kaljuvee in connection to the semester theme \textit{Interactive Systems Design}.

For an optimal understanding, this report should be read in chronological order. In the end of the report miscellaneous appendices are alphabetically listed named by a capital letter from A-Z, which is used for the referencing in the report text. Listed in the bibliography, found last in the report, are references to previous work. The method used for the referencing here is the ACM SIGCHI method. This method has references alphabetically ordered based on the first author’s last name. To reference a text or an image, the report refers to the number given by this order.

As a supplement to the report, an AV production has been made. This summarises the scope of the project and its findings. Also to be found is a link to the application along with an electronic version of the marker including instructions to the usage of the developed system. All of this is gathered in the attached zip folder.

In closing, we in the group wish to dedicate our thanks to each person who have contributed to the outcome of this project. First of all we want to thank VisitAalborg and Aalborg Guideforening for their willingness to assist us. Especially a huge thank you to Inge Vestergaard, our contact guide, without whom this project would not have been possible. Secondly, we thank all the participants who volunteered to participate in our evaluation. Finally, we would like to express our gratitude to our supervisor Ivan A. Nikolov and co-supervisor Claus B. Madsen for their commitment and constructive advisory throughout the entire project.